---
title: "Neoadjuvant vs. adivant chemotherapy in luminal B tumor-Before PS analysis Cohort 1"
author: "T Gaillard,E LAAS"
date: "18/05/2021"
header-includes:
- \usepackage{pdflscape}
- \usepackage{booktabs}
editor_options:
  chunk_output_type: console
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.path='Figures articles lum b aout/', dev = 'pdf',
 warning=FALSE, message=FALSE,  echo = FALSE, cache=F)
#, cache=TRUE, autodep = TRUE
```

```{r}

library(ggforce)
library(patchwork)
library(glue)
library(knitr)
library(magrittr)
library(rms)
library(RColorBrewer)
library(scales)
library(boot)
library(MatchIt) 
library(optmatch) 
library (Matching)
library (survminer)
library(ggsci)
library(ggpubr)
library(cowplot)
library(stddiff)
library(cobalt)
library(lubridate)


PROJECT_PATH_FONCTION = "/Users/enoralaas/Dropbox/articles/Luminaux neoadj/Luminaux/Fonctions/"
PROJECT_PATH_DATAS = "/Users/enoralaas/Dropbox/articles/Luminaux neoadj/Luminaux/data/"
source(file.path(PROJECT_PATH_FONCTION, "mes_fonctions2.R"))
source(file.path(PROJECT_PATH_FONCTION, "interaction.R"))


library(tidyverse)

```


```{r cohort 1}
load("d_imp4.RData") 

d_impFR <- subset(d_imp, d_imp$taille_cl == ">20")
d_impFR$BRCA_status <- NULL

d_impFR <- subset(d_impFR, d_impFR$chirax!="No")
d_impFR$chirax <- droplevels((d_impFR$chirax))
d_impFR$Grade_mod <- as.factor(ifelse (d_impFR$Grade == "1" |d_impFR$Grade=="2", "1-2","3"))

#on selectionne seulement les G3
d_impFR <- subset(d_impFR, d_impFR$Grade_mod == "3")  
#je supprime des patientes triples neg qui etaient passé à l'as
d_impFR <- subset(d_impFR, d_impFR$ROPCT>0 | d_impFR$RPPCT>0)#
d_impFR <- subset(d_impFR, d_impFR$anneediag<2012)



#creation de la variable de Tils en classe de 10
d_impFR$TILS_pre_2cl <- cut(d_impFR$TILS_pre, c(0,10,90), c("≤10", ">10"))
#creation de la variable de RP
d_impFR$RP_cl <- cut(d_impFR$RPPCT, c(0,20,101),include.lowest = TRUE, c("≤20", ">20"))


## Taille en classe
d_impFR$taille_cl <- as.factor(ifelse(d_impFR$taille_tum <= 50, "T2",
                                      ifelse(d_impFR$taille_tum > 50, "T3", NA)))
d_imp$FR$taille_cl <- as.factor(d_impFR$taille_cl)


d_impFR$base_label <-NA
d_impFR$base_label[d_impFR$base=="Adj"] <- "AC"
d_impFR$base_label[d_impFR$base=="CNA"] <- "NAC"
d_impFR$base_label <- as.factor(d_impFR$base_label)

d_impFR$age_cl <- factor(d_impFR$age_cl, levels = c("<40","≥40" ))

```


# Analysis before PS

```{r}
# !! a la CENSURE
km_suivi <- survfit (Surv (tps_deces, 1-deces) ~ base, data=d_impFR)
#survdiff(Surv (tps_deces, 1-deces) ~ base, data=d_impFR) 

#Médiane survie
km_survie <- survfit (Surv (tps_deces, deces) ~ base, data=d_impFR)

# survie à 3 et 5 ans
#summary(km_survie, c(36,60))

```

On a median follow up of 58.4 months in the AC group, and 62.6 months in the NAC group (p = 0.08) there were 76 deaths (55 in the AC group and 21 in the NAC group), 131 metastasis (93 in the AC group and 38 in the NAC gorup), and 23 loco regional recurrence (13 in the AC group and 10 in the NAC group).

## Kaplan-Meier - Survival curves




```{r KM OS population totale, fig.width=9,fig.height=12,autodep=FALSE}

source("univarieSP.R")
fit_os_sp   <- survfit(Surv( d_impFR$tps_deces, d_impFR$deces)	~ base,  data = d_impFR)
palette_jco  <- c(pal_jco("default")(10))


p_os_sp <- ggsurvplot(fit_os_sp,data=d_impFR, 
                               palette = palette_jco[1:2],
                              pval = TRUE,
                              pval.coord = c(15,0.01),
                              # legend = c(15, 0.10), 
                              xlim=c(0,100),
                              legend.title = "CT strategy", 
                              legend.labs = levels(d_impFR$base_label),
                               legend = c(0.2, 0.20) ,
                              risk.table = T , risk.table.fontsize = 6,
                     risk.table.y.text=TRUE, 
           font.legend = 15 , size = 1, 
                              censor=F, font.x = 16, font.y = 16,font.tickslab = 16, risk.table.title ="N at risk",risk.table.y.text.col = T)
    
                             p_os_sp$plot <- p_os_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Overall survival")+xlab("Time (months)")
                          
                              p_os_sp$table <-p_os_sp$table +  theme(plot.title = element_text(size = 15))

                               p_os_sp$table[["theme"]][["axis.line"]][["colour"]]     <- "white"
                               p_os_sp$table[["theme"]][["axis.ticks"]][["colour"]]    <- "white"
                               p_os_sp$table[["theme"]][["axis.text.x"]][["colour"]]   <- "white"
                               p_os_sp$table[["labels"]][["y"]]                        <- " "
                               p_os_sp$table[["labels"]][["x"]]   
					
#p_os_sp
```




```{r KM DFS population totale, fig.width=9,fig.height=12,autodep=FALSE}

fit_dfs_sp               <- survfit(Surv( d_impFR$tps_ssr, d_impFR$ssr_num)	~ base ,  data = d_impFR)
palette_jco  <- c(pal_jco("default")(10))


p_dfs_sp<- ggsurvplot(fit_dfs_sp,data=d_impFR, 
                               palette = palette_jco[1:2],
                              pval = TRUE,
                              pval.coord = c(15,0.01),
                              # legend = c(15, 0.10), 
                              xlim=c(0,100),
                              legend.title = "CT strategy", 
                              legend.labs = levels(d_impFR$base_label),
                               legend = c(0.2, 0.20) ,
                              risk.table = T , risk.table.fontsize = 6,
                     risk.table.y.text=TRUE, 
           font.legend = 15 , size = 1, 
                              censor=F, font.x = 16, font.y = 16,font.tickslab = 16, risk.table.title ="N at risk",risk.table.y.text.col = T)
    
                             p_dfs_sp$plot <- p_dfs_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Disease free survival")+xlab("Time (months)")
                          
                              p_dfs_sp$table <-p_dfs_sp$table +  theme(plot.title = element_text(size = 15))

                               p_dfs_sp$table[["theme"]][["axis.line"]][["colour"]]     <- "white"
                               p_dfs_sp$table[["theme"]][["axis.ticks"]][["colour"]]    <- "white"
                               p_dfs_sp$table[["theme"]][["axis.text.x"]][["colour"]]   <- "white"
                               p_dfs_sp$table[["labels"]][["y"]]                        <- " "
                               p_dfs_sp$table[["labels"]][["x"]]   
					
#p_dfs_sp
```




```{r KM DMFS population totale sp, fig.width=9,fig.height=12,autodep=FALSE}

fit_drfs_sp   <- survfit(Surv(d_impFR$tps_drfs, d_impFR$DRFS_evt)	~ base ,  data = d_impFR)
palette_jco  <- c(pal_jco("default")(10))


p_drfs_sp<- ggsurvplot(fit_drfs_sp,data=d_impFR, 
                               palette = palette_jco[1:2],
                              pval = TRUE,
                              # legend = c(0.6, 0.25), 
                              xlim=c(0,100),
                              legend.title = "CT strategy", 
                              legend.labs = levels(d_impFR$base_label) ,
                              legend = c(0.2, 0.20) ,
                               pval.coord = c(15,0.01),
                              pval.size = 4, 
                              risk.table = T , risk.table.fontsize = 6,
                     risk.table.y.text=TRUE, 
           font.legend = 15 , size = 1, 
                              censor=F, font.x = 16, font.y = 16,font.tickslab = 16, risk.table.title ="N at risk",risk.table.y.text.col = T)
    
                             p_drfs_sp$plot <- p_drfs_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Distant recurrence free survival")+xlab("Time (months)")
                          
                              p_drfs_sp$table <-p_dfs_sp$table +  theme(plot.title = element_text(size = 15))

                               p_drfs_sp$table[["theme"]][["axis.line"]][["colour"]]     <- "white"
                               p_drfs_sp$table[["theme"]][["axis.ticks"]][["colour"]]    <- "white"
                               p_drfs_sp$table[["theme"]][["axis.text.x"]][["colour"]]   <- "white"
                               p_drfs_sp$table[["labels"]][["y"]]                        <- " "
                               p_drfs_sp$table[["labels"]][["x"]]   
					
#p_drfs_sp
```

```{r FigA3ABC Figure KM regroupée avant SP,fig.width=18,fig.height=6,autodep=FALSE, echo=TRUE}
library(cowplot)

##attention les labels des figures sont utilisés dans les 2 figures d'interaction : à changer si je vuex m'en servir
list_g <- list()
list_g[[1]] <- p_dfs_sp
list_g[[2]] <- p_drfs_sp
list_g[[3]] <- p_os_sp


figA1 <- arrange_ggsurvplots(list_g, print = TRUE,   ncol = 3, nrow = 1)
figA1
#save_plot("KM avant SP dec2020.pdf", figA1, base_height=5, base_width=8)
```

# PS developpment

Variable included in the PS were : age, tumor size and nodal status

```{r création population SP}

#multi <- glm (base~age+BMI+rcs(taille_tum,5)+menop.f+Node_preop , data=d_impFR, family=binomial)
#stepAIC(multi,direction = "backward")

multi_def <- glm( base ~ age +  rcs(taille_tum,5) + Node_preop , family = binomial, data = d_impFR)

set.seed(1703)
PRED <- multi_def$fitted.values
d_impFR$PRED <- PRED

```


```{r variables utiles et figure de SP}

d_impFR$base_mod <-NA
d_impFR$base_mod[d_impFR$base=="Adj"] <- 0
d_impFR$base_mod[d_impFR$base=="CNA"] <- 1

d_impFR$w <- d_impFR$base_mod/d_impFR$PRED + (1 - d_impFR$base_mod)/(1 - d_impFR$PRED)
d_impFR$wt = pmin(d_impFR$w, quantile(d_impFR$w, 0.99))

d_impFR$base_mod <- factor(d_impFR$base, labels  =c( "ACT","NAC"))


d_impFR$age_rev <- cut(d_impFR$age, c(0, 40,50,100), include.lowest=TRUE, labels = c("<40","40-50", "≥50"))


plot_SP <- ggplot(d_impFR, aes(x = PRED, fill = base_label)) + geom_density(alpha = 0.5) + theme_bw()+theme (legend.title= element_blank())   + scale_fill_jco() + xlab("Propensity score") +ylab("")+scale_color_jco()+ guides(colour=FALSE)
```




```{r}
# varquali <- c("ageclasse.f","BMI_cl","menop.f", "taille_cl", "nuicc","Node_preop", "emb_piece", "surgery", "RT", "chirax", "Node_postop", "TILS_pre_cl")
# 
# varquanti <- c("age","BMI","taille_tum", "TILS_pre","TILS_post")
# 
d_impFR$base_cl <- as.factor(ifelse(d_impFR$base == "Adj", 0, 1))
# stddiff.numeric(d_impFR, gcol = 53, vcol = c(2,3,6, 11))
# stddiff.category(d_impFR, gcol = 53, vcol = c(4))

################


covs0 <- subset(d_impFR, select = c("age", "taille_tum",  "taille_cl", "Node_preop", "menop.f",   "BMI"))

v <- data.frame(old = c("age", "taille_tum","taille_cl", "Node_preop", "menop.f", 
                         "BMI" ),
                new = c("Age", "Tumor Size" , "T2-T3", "Preoperative Nodal status", 
                        "Menopausal status", "BMI"))

covplot <- love.plot(bal.tab(covs0, treat = d_impFR$base_cl, weights = d_impFR$wt,
        method = "weighting"), abs = T, threshold = 0.1, stars= "raw", line = F, grid = T,
         var.names = v, colors = c("#CD534CFF", "#003C67FF"))


#img = "/Users/enoralaas/Dropbox/articles/Luminaux neoadj/Luminaux/dider.png",


# eno <- love.plot(bal.tab(covs0, treat = d_impFR$base_cl, weights = d_impFR$wt,
#         method = "weighting"), abs = T, threshold = 0.1, stars= "raw", line = F, grid = T,
#         var.names = v, colors = c("#E7B800", "#2E9FDF"))+geom_image(aes(image = img))

```


```{r figA4AB ,fig.width=8,fig.height=3}
library(patchwork)


(plot_SP+covplot)

```
