---
title: "Neoadjuvant vs. adivant chemotherapy in luminal B tumor-Analysis before PS cohort 2"
author: "T Gaillard,E LAAS"
date: "18/05/2021"
header-includes:
- \usepackage{pdflscape}
- \usepackage{booktabs}
editor_options:
  chunk_output_type: console
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.path='Figures articles lum b aout/', dev = 'pdf',
 warning=FALSE, message=FALSE,  echo = FALSE, cache=F)
#, cache=TRUE, autodep = TRUE
```

```{r}

library(ggforce)
library(patchwork)
library(glue)
library(knitr)
library(magrittr)
library(rms)
library(RColorBrewer)
library(scales)
library(boot)
library(MatchIt) 
library(optmatch) 
library (Matching)
library (survminer)
library(ggsci)
library(ggpubr)
library(cowplot)
library(stddiff)
library(cobalt)
library(lubridate)


PROJECT_PATH_FONCTION = "/Users/enoralaas/Dropbox/articles/Luminaux neoadj/Luminaux/Fonctions/"
PROJECT_PATH_DATAS = "/Users/enoralaas/Dropbox/articles/Luminaux neoadj/Luminaux/data/"
source(file.path(PROJECT_PATH_FONCTION, "mes_fonctions2.R"))
source(file.path(PROJECT_PATH_FONCTION, "interaction.R"))


library(tidyverse)

```

# Analysis before PS

```{r cohort 1}
load("d_imp4.RData") 

d_impFR <- subset(d_imp, d_imp$taille_cl == ">20")
d_impFR$BRCA_status <- NULL

d_impFR <- subset(d_impFR, d_impFR$chirax!="No")
d_impFR$chirax <- droplevels((d_impFR$chirax))
d_impFR$Grade_mod <- as.factor(ifelse (d_impFR$Grade == "1" |d_impFR$Grade=="2", "1-2","3"))

#on selectionne seulement les G3
d_impFR <- subset(d_impFR, d_impFR$Grade_mod == "3")  
#je supprime des patientes triples neg qui etaient passé à l'as
d_impFR <- subset(d_impFR, d_impFR$ROPCT>0 | d_impFR$RPPCT>0)#
d_impFR <- subset(d_impFR, d_impFR$anneediag<2012)



#creation de la variable de Tils en classe de 10
d_impFR$TILS_pre_2cl <- cut(d_impFR$TILS_pre, c(0,10,90), c("≤10", ">10"))
#creation de la variable de RP
d_impFR$RP_cl <- cut(d_impFR$RPPCT, c(0,20,101),include.lowest = TRUE, c("≤20", ">20"))


## Taille en classe
d_impFR$taille_cl <- as.factor(ifelse(d_impFR$taille_tum <= 50, "T2",
                                      ifelse(d_impFR$taille_tum > 50, "T3", NA)))
d_imp$FR$taille_cl <- as.factor(d_impFR$taille_cl)


d_impFR$base_label <-NA
d_impFR$base_label[d_impFR$base=="Adj"] <- "AC"
d_impFR$base_label[d_impFR$base=="CNA"] <- "NAC"
d_impFR$base_label <- as.factor(d_impFR$base_label)

d_impFR$age_cl <- factor(d_impFR$age_cl, levels = c("<40","≥40" ))

```



```{r}
load("07_oncofertilite_consore_preprocessed_labels.RData")#n = 1357
oncofert <- database_preprocessed_labels
# load("/Users/enoralaas/Downloads/03_p53_eortc_preprocessed_labels.RData")#n = 1856
# basep53 <- database_preprocessed_labels
# load("/Users/enoralaas/Downloads/04_canto_preprocessed_labels.RData")#9510
# canto  <- database_preprocessed_labels
load("ki67_enora.RData")
ki <- ki67_enora

test <- read_csv2("oncofertilite_tumorec_vs_mastec_09042021.csv")

load("30_julie_subtype_preprocessed_labels.RData")
oncofert_compl <- database_preprocessed_labels

base <- left_join(oncofert,oncofert_compl, by = "numdos_curie")
base <- left_join(base,ki , by = "numdos_curie")
base <- left_join(base,test , by = "numdos_curie")
base <- subset(base, base$luminal.y == "Luminal")


d <- base[c("dat_first_surg", "dat_os", 
"database", "numdos_curie", "cletri", "base_cletri", "dat_birth", 
"year_birth", "dat_bc_diagnosis", "year_diag", "period_diag", 
"center_curie",   "age", "age_cl_10_1", 
"age_cl_10_2", "age_cl_3_cl", "age_cl_5_cl", "age_young_cl", 
"age_young_cl_30_bin", "age_young_cl_40_bin", "age_young_cl_45_bin", 
"age_young_cl_50_bin", "nb_child", "nb_child_3cl", "prev_child", 
"brca_screen", "brca_mut", "brca_1_2_mut", "weight", "size", 
"bmi", "bmi_2cl", "bmi_3cl", "bmi_4cl", "bmi_5cl", "smoking", 
"bilat_bc", "inflammatory_bc", "tclin", "ctuicc_3cl", "ctuicc_2cl", 
"cnuicc_4cl", "cnuicc_2cl", "muicc", "dat_first_biopsy", 
"histo_3cl", "histo_2cl", "grade_3cl", "grade_2cl", "ct", "dat_first_ct", 
"neo_ct", "adj_ct", "ct_setting_5cl.x", "nbggpos", "pnuicc_4cl", 
"histo_size", "pcr", "nbggpos_postneo", "ypnuicc_4cl", "ypnuicc_3cl", 
"ypnuicc_2cl", "dat_last_update", "ev_recloc", "ev_recloc_txt", 
"dat_recloc", "ev_recreg", "ev_recreg_txt", "dat_recreg", "ev_meta", 
"ev_meta_txt", "dat_meta", "ev_contro", "ev_contro_txt", "dat_contro", 
"ev_secondk", "ev_secondk_txt", "dat_secondk", "status_vital", 
"status_vital_txt", "cause_death", "dat_last_news", "dat_last_news_censor", 
"year_last_news", "status_rfs_diag", "status_rfs_diag_txt", "status_drfs_diag", 
"status_drfs_diag_txt", "status_dss_diag", "status_dss_diag_txt", 
"delay_rfs_diag", "delay_drfs_diag", "delay_dss_diag", "delay_os_diag", 
"status_dfs", "status_dfs_txt", "dat_rfs", "dat_drfs", "dat_dfs", 
"dat_dss","er_status", "pr_status", "hr_status","conclusion_KI_tum_non_traitee" ,"tumorectomy_or_mastectomy" )]


d$ki <- as.numeric(d$conclusion_KI_tum_non_traitee)
d$surgery<-as.factor(d$tumorectomy_or_mastectomy)


#dd <- subset(d, d$ctuicc_3cl != "T0-T1")
dd <- subset(d, d$tclin > 20)
dd <- subset(dd, dd$grade_2cl == "Grade III")

dd$ctuicc_3cl <- droplevels(dd$ctuicc_3cl)
# age médian : 37 ans
dd$age_young_cl_35_bin <- as.factor(ifelse(dd$age < 35, 0, 1))
levels(dd$age_young_cl_35_bin) <- c("[0-35)", "35+")
dd$chimio <- as.factor(ifelse (dd$neo_ct == "Yes", "NAC", "AC"))
dd$age_cl_10_1 <- droplevels(dd$age_cl_10_1)
dd$surgery <- factor(dd$surgery, labels = c("mastectomy",  "tumorectomy", NA, NA))

dd$date_anne <- year(dd$dat_first_surg)

#j'enleve les patientes en commun
dd <-tibble(dd) %>% filter(!(dd$numdos_curie %in% d_impFR$numdos))

```

```{r}
(km_suivi <- survfit (Surv (delay_os_diag, 1-status_vital) ~ chimio, data=dd))
survdiff(Surv (delay_os_diag, 1-status_vital) ~ chimio, data=dd) 
```


On a median follow up of 55 months in the AC group, and 60 months in the NAC group, we recorded : 4 local recurrences (all in the NAC group), 4 regional recurrences (all in the NAC group), 27 distant recurrence (19 in the NAC group and 8 in the AC group) and 16 death (12 in the NAC group and 5 in the AC group)


# KM sans pondération

```{r Figure KM , fig.height=6, fig.width=18, autodep=FALSE}

fit_os_sp   <- survfit(Surv( delay_os_diag, status_vital)	~ chimio,  data = dd)
palette_jco  <- c(pal_jco("default")(10))


p_os_sp <- ggsurvplot(fit_os_sp,data=dd, 
                               palette = palette_jco[1:2],
                              pval = TRUE,
                              pval.coord = c(15,0.01),
                              # legend = c(15, 0.10), 
                              xlim=c(0,100),
                              legend.title = "CT strategy", 
                              legend.labs = levels(dd$chimio),
                              legend = c(0.2, 0.20) ,
                              risk.table = T , risk.table.fontsize = 6,
                     risk.table.y.text=TRUE, 
           font.legend = 15 , size = 1, 
                              censor=F, font.x = 16, font.y = 16,font.tickslab = 16, risk.table.title ="N at risk",risk.table.y.text.col = T)
    
                              p_os_sp$plot <- p_os_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Overall survival")
                              p_os_sp$table <-p_os_sp$table +  theme(plot.title = element_text(size = 10)) 
                              
 p_os_sp$plot <- p_os_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Overall survival")+xlab("Time (months)")
                          
                              p_os_sp$table <-p_os_sp$table +  theme(plot.title = element_text(size = 15))

                               p_os_sp$table[["theme"]][["axis.line"]][["colour"]]     <- "white"
                               p_os_sp$table[["theme"]][["axis.ticks"]][["colour"]]    <- "white"
                               p_os_sp$table[["theme"]][["axis.text.x"]][["colour"]]   <- "white"
                               p_os_sp$table[["labels"]][["y"]]                        <- " "
                               p_os_sp$table[["labels"]][["x"]]   
					
                               

fit_dfs_sp               <- survfit(Surv(delay_rfs_diag, status_rfs_diag)	~ chimio ,  data = dd)
palette_jco  <- c(pal_jco("default")(10))


p_dfs_sp<- ggsurvplot(fit_dfs_sp,data=dd, 
                               palette = palette_jco[1:2],
                              pval = TRUE,
                               pval.coord = c(15,0.01), 
                              xlim=c(0,100),
                              legend.title = "CT strategy", 
                              legend.labs = levels(dd$chimio) ,
                              legend = c(0.2, 0.20) ,
                              risk.table = T , risk.table.fontsize = 6,
                     risk.table.y.text=TRUE, 
           font.legend = 15 , size = 1, 
                              censor=F, font.x = 16, font.y = 16,font.tickslab = 16, risk.table.title ="N at risk",risk.table.y.text.col = T)
     p_dfs_sp$plot <- p_dfs_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Disease free survival")+xlab("Time (months)")
                          
                              p_dfs_sp$table <-p_dfs_sp$table +  theme(plot.title = element_text(size = 15))

                               p_dfs_sp$table[["theme"]][["axis.line"]][["colour"]]     <- "white"
                               p_dfs_sp$table[["theme"]][["axis.ticks"]][["colour"]]    <- "white"
                               p_dfs_sp$table[["theme"]][["axis.text.x"]][["colour"]]   <- "white"
                               p_dfs_sp$table[["labels"]][["y"]]                        <- " "
                               p_dfs_sp$table[["labels"]][["x"]]   

                              
                              
fit_drfs_sp   <- survfit(Surv(delay_drfs_diag, status_drfs_diag)	~ chimio ,  data = dd)
palette_jco  <- c(pal_jco("default")(10))


p_drfs_sp<- ggsurvplot(fit_drfs_sp,data=dd, 
                               palette = palette_jco[1:2],
                              pval = TRUE,
                       pval.coord = c(15,0.01),
                              # legend = c(0.6, 0.25), 
                              xlim=c(0,100),
                              legend.title = "CT strategy", 
                              legend.labs = levels(dd$chimio) ,
                             legend = c(0.2, 0.20) ,
                              risk.table = T , risk.table.fontsize = 6,
                     risk.table.y.text=TRUE, 
           font.legend = 15 , size = 1, 
                              censor=F, font.x = 16, font.y = 16,font.tickslab = 16, risk.table.title ="N at risk",risk.table.y.text.col = T)
    
                              p_drfs_sp$plot <- p_drfs_sp$plot + theme(plot.title = element_text(hjust = 0.5))+ ylab("Distant recurrence free survival")+xlab("Time (months)")
                          
                              p_drfs_sp$table <-p_dfs_sp$table +  theme(plot.title = element_text(size = 15))

                               p_drfs_sp$table[["theme"]][["axis.line"]][["colour"]]     <- "white"
                               p_drfs_sp$table[["theme"]][["axis.ticks"]][["colour"]]    <- "white"
                               p_drfs_sp$table[["theme"]][["axis.text.x"]][["colour"]]   <- "white"
                               p_drfs_sp$table[["labels"]][["y"]]                        <- " "
                               p_drfs_sp$table[["labels"]][["x"]] 
```    

```{r FigA7ABC Figure KM regroupée, fig.height=6, fig.width=18, autodep=FALSE}
list_g <- list()
list_g[[1]] <- p_dfs_sp
list_g[[3]] <- p_os_sp
list_g[[2]] <- p_drfs_sp

arrange_ggsurvplots(list_g, print = TRUE,   ncol = 3, nrow = 1)


```

# Propensity score

Variables included in the PS were : 
age, initial clinical tumor size and initial nodal status

```{r  création population SP}
# on rappelle que toutes les variables quantitatives sont lineaires
dnona <- subset(dd, !is.na(dd$bmi))
multi <- glm (chimio~age+ bmi +tclin+cnuicc_2cl , data=dnona, family=binomial)
library(MASS)
stepAIC(multi,direction = "backward")

multi_def <- glm( chimio ~ age  + tclin + cnuicc_2cl , family = binomial, data = dd)

set.seed(1703)
PRED <- multi_def$fitted.values
dd$PRED <- PRED


dd$base_mod <-NA
dd$base_mod[dd$chimio=="AC"] <- 0
dd$base_mod[dd$chimio=="NAC"] <- 1



dd$w <- dd$base_mod/dd$PRED + (1 - dd$base_mod)/(1 - dd$PRED)
dd$wt = pmin(dd$w, quantile(dd$w, 0.99))



plot_SP <- ggplot(dd, aes(x = PRED, fill = chimio)) + geom_density(alpha = 0.5) +theme (legend.title= element_blank())  +  guides(colour=FALSE) + scale_fill_jco() + xlab("Propensity score") +ylab("")
```


```{r , fig.width= 14, fig.height=10}
dd$base <- as.factor(ifelse(dd$base_mod == 0, 0, 1))
dd <- subset(dd, !is.na(dd$bmi))

covs0 <- subset(dd, select = c("age", "tclin", "ctuicc_3cl", "cnuicc_2cl", "bmi"))

v <- data.frame(variable = c("age", "tclin", "ctuicc_3cl", "cnuicc_2cl", "bmi"),
                name_variable = c("Age", "Tumor size",  "T2-T3", "Preoperative Nodal status", "BMI"))

lovplot <- love.plot(bal.tab(covs0, treat = dd$base, weights = dd$wt, method = "weighting"), abs = T, threshold = 0.1, stars= "raw", line = F, grid = T, var.names = v,   colors = c("#CD534CFF", "#003C67FF"))
```


```{r FigA8AB,fig.width=8,fig.height=3}
library(patchwork)


(plot_SP+lovplot)

```

